\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual Multi-Loop Integrands

### 2023-09-21 notes/2loopNLSM.tex
Tried to fix all l -> \ell in main text.

\subsection{One-loop color-dual integrands}\label{oneLoopCK}
Our first application of this theory for color-dual construction at
loop level is for self-dual Yang-Mills (SDYM). At tree-level, the
off-shell cubic vertices can be written in terms of light cone
coordinates \cite{Monteiro2011pc}:
\begin{equation}
X(p,k) = p_u k_w-p_w k_u
\end{equation}
At loop-level, this construction needs to be analytically continued to
general dimension in order to apply dimensional regularization at
one-loop. This can be done using the cubic semi-YM vertices of the
previous section:
\begin{equation} \label{DdimSDYM}
\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= \mathcal{X}(k_1,k_2) = (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3) -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3)
\end{equation}
Plugging in on-shell all-plus helicity states in light-cone gauge will
yield precisely the 4D SDYM vertex, up to an unphysical phase:
  \be
  \mathcal{X}(k^+_1,k^+_2) = \frac{\langle 12\rangle^3}{ \langle23\rangle \langle 31\rangle} \sim \langle 12\rangle = k_{1,u} k_{2,w}-k_{1,w} k_{2,u}
 \ee
where $\mathcal{X}(k^+_1,k^+_2) = A^{\text{YM}}(1^+,2^+,3^-)$ in light cone gauge, and in the second step applied momentum conservation to redefinition of the spinor bracket, $\langle 12\rangle \rightarrow X(p,k)$ defined in \cref{Conventions}. Of course, the form of \cref{DdimSDYM} has the advantage of
permitting a $D$-dimensional construction of the one-loop
integrand. Below we provide a four-point example:
\begin{equation}
\simplebox = g_{\text{YM}}^4 \langle \mathcal{X}(k_1,l_1)\mathcal{X}(k_2,l_2)\mathcal{X}(k_3,l_3)\mathcal{X}(k_4,l_4)\rangle
\end{equation}
where $l_i = l+k_1+k_2+\cdots+ k_i$ and the bracket $\langle \,\cdots\rangle$ indicates that we have applied the gauge fixed state projector, $\sum {\varepsilon^\mu_{(+l_i)}\varepsilon^\nu_{(-l_i)}}=\eta^{\mu\nu}$ on all internal polarizations. In general, the $n$-gon diagram would be,
\begin{equation}
N^{\text{SDYM}}_{n\text{-gon}}= \nGonVector = g_{\text{YM}}^n \langle \mathcal{X}(k_1,l_1)\mathcal{X}(k_2,l_2)\cdots \mathcal{X}(k_n,l_n) \rangle
\end{equation}
Due to the state-sum of internal loop factors,
$\sum {\varepsilon_{(+l)}\varepsilon_{(-l)}}\sim D$, the integrand above
depends explicitly on the spacetime dimension, $D$. By taking a
derivative\footnote{Another way to understand this derivative is that
  it selects the large $D$ behavior of the integrand.}, we can recover
the integrand needed for all-plus one-loop amplitudes with an internal
scalar:
\begin{equation}
\partial_D N^{\text{SDYM}}_{n\text{-gon}}=\nGonScalar  = (2 g_{\text{YM}})^n (l_1 \varepsilon_1)(l_2 \varepsilon_2)\cdots (l_n \varepsilon_n)
\end{equation}
This integrand numerator with internal scalar loop is precisely what
one would obtain from the Feynman rules of $YZ$-theory, absent the $\bar{Z}Z$
internal vector loop. For more background, we refer the reader to
\cref{sec:CKLagrangians}. When plugging on the on-shell states of $YZ$-theory, we thus obtain the following expression for the NLSM one-loop $n$-gon numerator:
\begin{equation}
N^{\text{NLSM}}_{n\text{-gon}}=\left[\partial_D  N^{\text{SDYM}}_{n\text{-gon}}\right]^{\epsilon \rightarrow k}=\nGonScalar =  f_\pi^{-n} [12][23]\cdots [n1]
\end{equation}
Where we have define the antisymmetric kinematic variable, $[ij] = l_i^2 - l_j^2$, since when plugging on longitudinal modes, the $n$-gon can be re-expressed completely in terms of inverse propagators, $2(k_i \cdot l_i) = l_{i}^2-l^2_{i-1}$. We have verified through 10-point one-loop that this $n$-gon expression is a valid color-dual representation for NLSM.

>>>>

\subsection{One-loop color-dual integrands}\label{oneLoopCK}
Our first application of this theory for color-dual construction at
loop level is for self-dual Yang-Mills (SDYM). At tree-level, the
off-shell cubic vertices can be written in terms of light cone
coordinates \cite{Monteiro2011pc}:
\begin{equation}
X(p,k) = p_u k_w-p_w k_u
\end{equation}
At loop-level, this construction needs to be analytically continued to
general dimension in order to apply dimensional regularization at
one-loop. This can be done using the cubic semi-YM vertices of the
previous section:
\begin{equation} \label{DdimSDYM}
\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}= \mathcal{X}(k_1,k_2) = (\varepsilon_1\bar{\varepsilon}_3)(\varepsilon_2 k_3) -  (\varepsilon_2\bar{\varepsilon}_3)(\varepsilon_1 k_3)
\end{equation}
Plugging in on-shell all-plus helicity states in light-cone gauge will
yield precisely the 4D SDYM vertex, up to an unphysical phase:
  \begin{equation}
  \mathcal{X}(k^+_1,k^+_2) = \frac{\langle 12\rangle^3}{ \langle23\rangle \langle 31\rangle} \sim \langle 12\rangle = k_{1,u} k_{2,w}-k_{1,w} k_{2,u}
 \end{equation}
where $\mathcal{X}(k^+_1,k^+_2) = A^{\text{YM}}(1^+,2^+,3^-)$ in light cone gauge, and in the second step applied momentum conservation to redefinition of the spinor bracket, $\langle 12\rangle \rightarrow X(p,k)$ defined in \cref{Conventions}. Of course, the form of \cref{DdimSDYM} has the advantage of
permitting a $D$-dimensional construction of the one-loop
integrand. Below we provide a four-point example:
\begin{equation}
\simplebox = g_{\text{YM}}^4 \langle \mathcal{X}(k_1,\ell_1)\mathcal{X}(k_2,\ell_2)\mathcal{X}(k_3,\ell_3)\mathcal{X}(k_4,\ell_4)\rangle
\end{equation}
where $\ell_i = \ell-(k_1+k_2+\cdots+ k_i)$ and the bracket $\langle \,\cdots\rangle$ indicates that we have applied the gauge fixed state projector, $\sum {\varepsilon^\mu_{(+\ell_i)}\varepsilon^\nu_{(-\ell_i)}}=\eta^{\mu\nu}$ on all internal polarizations. In general, the $n$-gon diagram would be,
\begin{equation}
N^{\text{SDYM}}_{n\text{-gon}}= \nGonVector = g_{\text{YM}}^n \langle \mathcal{X}(k_1,\ell_1)\mathcal{X}(k_2,\ell_2)\cdots \mathcal{X}(k_n,\ell_n) \rangle
\end{equation}
Due to the state-sum of internal loop factors,
$\sum {\varepsilon_{(+\ell)}\varepsilon_{(-\ell)}}\sim D$, the integrand above
depends explicitly on the spacetime dimension, $D$. By taking a
derivative\footnote{Another way to understand this derivative is that
  it selects the large $D$ behavior of the integrand.}, we can recover
the integrand needed for all-plus one-loop amplitudes with an internal
scalar:
\begin{equation}
\partial_D N^{\text{SDYM}}_{n\text{-gon}}=\nGonScalar  = (2 g_{\text{YM}})^n (\ell_1 \varepsilon_1)(\ell_2 \varepsilon_2)\cdots (\ell_n \varepsilon_n)
\end{equation}
This integrand numerator with internal scalar loop is precisely what
one would obtain from the Feynman rules of $YZ$-theory, absent the $\bar{Z}Z$
internal vector loop. For more background, we refer the reader to
\cref{sec:CKLagrangians}. When plugging on the on-shell states of $YZ$-theory, we thus obtain the following expression for the NLSM one-loop $n$-gon numerator:
\begin{equation}
N^{\text{NLSM}}_{n\text{-gon}}=\left[\partial_D  N^{\text{SDYM}}_{n\text{-gon}}\right]^{\epsilon \rightarrow k}=\nGonScalar =  f_\pi^{-n} [12][23]\cdots [n1]
\end{equation}
Where we have define the antisymmetric kinematic variable,
$[ij] = \ell_i^2 - \ell_j^2$, since when plugging on longitudinal
modes, the $n$-gon can be re-expressed completely in terms of inverse
propagators, $2(k_i \cdot \ell_i) = \ell_{i}^2-\ell^2_{i-1}$. We have
verified through 10-point one-loop that this $n$-gon expression is a
valid color-dual representation for NLSM.
